---
title: "Voting and Postcards"
author: Naveed Ahmad
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
library(dplyr)
library(knitr)
library(marginaleffects)
library(ggplot2)
```
## Summary
Whether voting behavior of people may be influenced through planed watching them. In this study it has been checked by using data from the paper "Social Pressure and Voter Turnout: Evidence from a Large-Scale Field Experiment" by Gerber, Green, and Larimer (2008). However, the data used in this study is from Michigan which may not hold good for broader population in U.S. I have used the logistic regression model for predicting voter turnout as function of postcard treatment with covariates of age and sex. Tratement neighbors have the highest effect on vouter outcome.

## Statistical Model

$$P(Y = 1) = \frac{1}{1 + e^{-(\beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n)}}$$

with $Y \sim \text{Bernoulli}(\rho)$ where $\rho$ is the probability above.


```{r}
x <- shaming |> 
  mutate(civ_engage = primary_00 + primary_02 + primary_04 + 
               general_00 + general_02 + general_04) |> 
  select(primary_06, treatment, sex, age, civ_engage) |> 
  mutate(voter_class = factor(
    case_when(
      civ_engage %in% c(5, 6) ~ "Always Vote",
      civ_engage %in% c(3, 4) ~ "Sometimes Vote",
      civ_engage %in% c(1, 2) ~ "Rarely Vote"),
         levels = c("Rarely Vote", 
                    "Sometimes Vote", 
                    "Always Vote"))) |>
  mutate(voted = as.factor(primary_06))

```

```{r}
#| cache: true
fit_vote <- logistic_reg(engine = "glm") |>
  fit(voted ~ age + sex + treatment * voter_class, data = x)
```

## Fitted Logistic Regression Model (Compact Form)
This is our data Generating Mechanism
$$
\hat{Y} = \frac{1}{1 + e^{-(
\beta_0 + \sum_{j=1}^{p} \beta_j X_j
)}}
$$

where each $\beta_j~[CI_{low},~CI_{high}]$ is:

- $\beta_0 = -2.43~[-2.48,\ -2.39]$ (Intercept)  
- $\beta_1 = 0.01~[0.01,\ 0.01]$ (age)  
- $\beta_2 = 0.04~[0.02,\ 0.05]$ (sexMale)  
- $\beta_3 = 0.09~[-0.00,\ 0.17]$ (treatmentCivicDuty)  
- $\beta_4 = 0.07~[-0.02,\ 0.16]$ (treatmentHawthorne)  
- $\beta_5 = 0.20~[0.12,\ 0.29]$ (treatmentSelf)  
- $\beta_6 = 0.36~[0.28,\ 0.44]$ (treatmentNeighbors)  
- $\beta_7 = 0.82~[0.78,\ 0.86]$ (voterClassSometimes)  
- $\beta_8 = 1.61~[1.57,\ 1.65]$ (voterClassAlways)  
- $\beta_9 = 0.03~[-0.06,\ 0.12]$ (CivicDuty × Sometimes)  
- $\beta_{10} = 0.06~[-0.03,\ 0.15]$ (Hawthorne × Sometimes)  
- $\beta_{11} = 0.05~[-0.04,\ 0.14]$ (Self × Sometimes)  
- $\beta_{12} = 0.04~[-0.05,\ 0.13]$ (Neighbors × Sometimes)  
- $\beta_{13} = -0.05~[-0.15,\ 0.05]$ (CivicDuty × Always)  
- $\beta_{14} = 0.06~[-0.04,\ 0.16]$ (Hawthorne × Always)  
- $\beta_{15} = -0.01~[-0.10,\ 0.09]$ (Self × Always)  
- $\beta_{16} = 0.01~[-0.09,\ 0.10]$ (Neighbors × Always)

## Logestic Regression Coefficients
```{r}
model_tbl <- tidy(fit_vote, conf.int = TRUE)
 model_tbl %>%
  select(term, estimate, conf.low, conf.high) %>%
  mutate(across(c(estimate, conf.low, conf.high), ~ round(.x, 2))) %>%
  rename(
    Term = term,
    Estimate = estimate,
    `95% CI Lower` = conf.low,
    `95% CI Upper` = conf.high
  ) %>%
  kable(caption = "Logistic Regression Coefficients with 95% Confidence Intervals")
```

```{r}
plot_data <- plot_predictions(fit_vote, type = "prob", condition = c("treatment", "voter_class"), draw = FALSE)
```

